The process of retrieving schedule data from the Novasoftware web application

### 2016-04-18 paper/paper.tex
Cleaned up project

	\section{Introduction and background}
	I have observed that many Swedish schools including Värmdö Gymnasium, the high school that I attend, rely on the Novasoftware schedule application. I have further recognized that there is a general consensus among students that the web based schedule viewer provided with it does not reach the expectations of a modern application, especially considering its design and mobile experience. Because of this it may be of interest to create another viewing application, satisfying the needs of a modern such, using the schedule data provided by Novasoftware. Beacause Novasoftware provides no public API (Application Programming Interface) or other simple way of extracting this data, a method of obtaining the information from the provided public interfaces is required.

>>>>

	\section{Introduction and background}
	I have observed that many Swedish schools including Värmdö Gymnasium, the high school that I attend, rely on the Novasoftware schedule application. I have further recognized that there is a general consensus among students that the web based schedule viewer provided with it does not reach the expectations of a modern application, especially considering its design and mobile experience. Because of this it may be of interest to create another viewing application, satisfying the needs of a modern application, using the schedule data provided by Novasoftware. Beacause Novasoftware provides no public API (Application Programming Interface) or other simple ways of extracting this data, a method of obtaining the information from the provided public interfaces is required.
